Two-component thermal dust emission model: application to the Planck HFI maps

### 2013-12-12 ms.tex
more sub-sections added to outline, bibliography included, other clean-up

\begin{abstract}
We have fit the FDS99 two-component dust emission model over
the full sky, based on dust SEDs comprised of  Planck HFI and IRAS 100$\mu$m. 
As a result, we have obtained maps of optical depth $\tau_{545}$ and dust 
temperatures $T_1$ and $T_2$,  with angular resolution  $\sim$6$'$. These maps 
serve as an interesting comparison to alternative models, for example 
one-component models with varying $T$ and $\beta$. We also expect the derived 
optical depth to be useful as a cross-check for other extinction estimates, 
such as the SFD98 map, which assumed $\beta = 2$ single-component dust 
emission, as well as forthcoming dust maps based on observations of stars in 
the optical rather than infrared emission.
\end{abstract}

@@

To add information about the dust emission on the Wien side of its spectrum,
we include IRAS 100$\mu$m. We use the SFD reprocessing of IRAS 100$\mu$m, which
we will refer to as \verb|i100| (Schegel et al. 1998). \verb|i100|
\section{Pre-processing}

@@

\section{Model}
Our model is that of FDS99, which consists of two populations of dust 
grain emitting as modified blackbodies, but with different temperatures
and different power law emissivities $\beta$.

@@

>>>>

\begin{abstract}
We have fit the \cite{FDS99} two-component dust emission model over
the full sky, based on Galactic dust SEDs composed of  Planck HFI and \cite{SFD} 
\IRAS~100$\mu$m. As a result, we have obtained maps of dust optical depth $\tau_{545}$ 
and temperatures $T_1$ and $T_2$,  with angular resolution  $\sim$6$'$. These maps 
serve as an interesting comparison to alternative models, for example 
one-component models with varying $T$ and $\beta$. We also expect the derived 
optical depth to be useful as a cross-check for other extinction estimates, 
such as the SFD98 map, which assumed $\beta = 2$ single-component dust 
emission, as well as forthcoming dust maps based on observations of stars in 
the optical rather than infrared emission. %mention the enhanced temperature resolution relative
% to SFD
\end{abstract}

@@

To add information about the dust emission on the Wien side of its spectrum,
we include IRAS 100$\mu$m. We use the SFD reprocessing of IRAS 100$\mu$m, which
we will refer to as \verb|i100| (Schegel et al. 1998). \verb|i100|

\section{Pre-processing}

@@

\subsection{Point Sources}

\section{Model}
Our model is that of FDS99, which consists of two populations of dust 
grain emitting as modified blackbodies, but with different temperatures
and different emissivity power law indices $\beta$.

@@

\section{Conclusion}

Based on observations obtained with Planck (http://www.esa.int/Planck), 
an ESA science mission with instruments and contributions directly funded 
by ESA Member States, NASA, and Canada.

\bibliographystyle{apj}
\bibliography{twocomp.bib}
